Contextual Combinatorial Cascading Bandits

### 2016-01-20 contextual combinatorial cascading bandits.tex
update proof and sub-Gaussion

\newcommand{\CLemmaPrefixExi}{
	Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0$. Let $A = (a_1, ..., a_{\abs{A}})$. For the time $t$ and the conjunctive objective, there exists a prefix $B$ of $A$ such that 
	$$
	p_{t, B} \geq \frac{1}{2}f_{t}^{\ast} - 1 + \gamma_{\abs{B}}, \qquad R(t, B) \geq \frac{1}{2} R(t, A).
	$$ 
}
\newcommand{\CLemmaSumXiEstimateInDet}{
  If $\lambda \geq C_\gamma$, then
  $$
    \sum_{s=1}^t \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2\ln \left(\frac{\det(\bV_t)}{\lambda^d} \right).
  $$
}
\newcommand{\CLemmaDetVt}{
  $\det(\bV_t)$ is increasing with respect to $t$ and 
  $$
    \det(\bV_t) \leq (\lambda + C_\gamma t/d)^d.
  $$
}

@@

@@

The main contributions of this paper can be listed as follows: (1) We propose a general framework called contextual combinatorial cascading bandit that can address recommendation problem and network routing problem; (2) We propose $C^3$-UCB, an efficient algorithm for contextual combinatorial cascading bandit, with regret bound as $\tilde{O}(\sqrt{T})$ for $T$ rounds; (3) We evaluate this algorithm on synthetic data, recommendation data and network routing data and the results show that our algorithm is effective.

@@

Our work generalizes combinatorial cascading bandits of \cite{kveton2015combinatorial} to involve contextual information and position discount. Our generalization expands the applicability of this model and we evaluate it on two real-world problems. \cite{kveton2015cascading} introduced the cascading model to the multi-armed bandit framework and the feasible set is a uniform matroid. They found that recommending items in increasing order of their UCBs has a better performance than in decreasing order of their UCBs. To improve the quality of user experience, it is natural to list items with higher preference first and then lower preference items. Our work extends this part by introducing position discounted parameters. Under our setting, the items with higher UCB will come first. \cite{combes2015learning} considers a similar recommendation model to cascading bandits with position discount but they assume that a user is interested in a single topic only. In our setting, users and items are represented by feature vectors which is more general.

Our work considers contextual combinatorial bandits with cascading feedback and nonlinear reward. \cite{li2010contextual} studied multi-armed bandit with context information. \cite{qin2014contextual} introduced contextual combinatorial bandit with semi-bandit feedback and nonlinear reward. Their setting is more informative than ours but our algorithm is competitive to theirs.

@@

A newer version of \cite{chen2013combinatorial} considers probabilistic triggering base arms in stochastic combinatorial semi-bandit

@@

Let $\cH_t$ denote the history before the learning agent chooses action at time $t$. Thus $\cH_t$ contains all information as well as observations at time $s < t$ and context information at time $t$. Given history $\cH_t$, we assume $\bw_{t,a}$'s are mutually independent and satisfy
\begin{equation} % eq:expectation
  \label{eq:expectation}
  \EE[\bw_{t,a} | \cH_t] = \theta_{\ast}^{\top} x_{t,a},
\end{equation}
where $\theta_{\ast}$ is an unknown $d$-dimensional vector with the assumption that $\norm{\theta_{\ast}}_2 \leq 1$ and $0 \leq \theta_{\ast}^{\top} x_{t,a} \leq 1$ for all $t, a$. Define $w_{t,a} = \theta_{\ast}^{\top} x_{t,a}$ as the expected weight of base arm $a$ at time $t$.

@@

\begin{lemma} $\mathrm{\cite{abbasi2011improved}}$ %estimate of theta
  \label{thm:theta_estimate}
  Let 
  \begin{equation}
    \bbeta_{t}(\delta) = \sqrt{\ln\left(\frac{\det(\bV_{t})}{\lambda^d \delta^2}\right)} + \sqrt{\lambda}. \label{eq:definebeta}
  \end{equation}
  Then for any $\delta > 0$, with probability at least $1 - \delta$, for all $t > 0$, we have
  \begin{equation}
    \label{eq:estimateTheta}
    \norm{\hat{\theta}_t - \theta_{\ast}}_{\bV_{t}} \leq \bbeta_{t}(\delta).
  \end{equation}
\end{lemma}

@@

\begin{theorem} %main theorem
	\label{thm:main}
	Suppose the expected reward function $f(A, w)$ is a function of expected weights and satisfies the requirements of monotonicity and Lipschitz continuity. Assume there is an $\alpha$-approximation oracle $\cO_{\cS}$. Then for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regret of our algorithm, C$^3$-UCB, satisfies
	\begin{align}
		R(n) &\le \frac{\sqrt{2}}{p^*} \sqrt{TKd\ln(1 + C_\gamma n/(\lambda d))}  \nonumber \\
		&\qquad \cdot \left(\sqrt{d\ln \left( \frac{1 + C_\gamma n/(\lambda d)}{\delta^{2/d}}\right) } + \sqrt{\lambda}\right) \nonumber \\
		&=O\left(\frac{d}{p^*} \sqrt{nK} \ln \left(\frac{C_\gamma n}{\delta^{2/d}}\right) \right).
	\end{align}
\end{theorem}
\begin{proof} [of Theorem \ref{thm:main}] %proof outline of main theorem
	The complete proof is in the Appendix. The main idea is to reduce the regret at time $t$, $R(t, \bA_t)$, to the case that all items in $\bA_t$ have been observed. In particular,
	\begin{align*}
    	&\EE[R(t, \bA_t)|\cH_t] \\
    	&\qquad = \EE \left[ \left. R(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t = \abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right]\\
    	&\qquad \leq \frac{1}{p^*} \EE \left[ \left. R(t, \bA_t) \bOne\{\bO_t = \abs{\bA_t}\} \right| \cH_t \right].
    % &\EE_t[R_{\wedge}(t, \bA_t)] \\
    % &\qquad \EE \left[ \left. R_{\wedge}(t, \bA_t) \EE \left[ \left. \frac{1}{p_{\wedge, t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right] \\
    \end{align*}
    Also, by monotonicity and Lipschitz continuity,
    $$
    	R(t, \bA_t) \leq B \sqrt{\sum_{k=1}^{\bO_t} \bbeta_{t-1}(\delta) \| \gamma_k x_{t, \ba_k^t} \|_{\bV_{t-1}}^2}
    $$

	% our analysis to that of CombCascade in \cite{kveton2015combinatorial}. This reduction is challenging for two reasons. First, our setting has contextual information. Second, we consider position-discounted weight $\gamma$.

	% Our analysis can be trivially reduced to contextual combinatorial semi-bandits by conditioning on the event of observing all items. Then we can express the expected regret at time $t$ conditioned on the history $\cH_t$ as:
	% \begin{align*}
 %    	&\EE[R(t, \bA_t)|\cH_t] \\
 %    	&\qquad = \EE \left[ \left. R(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right],\\
 %    % &\EE_t[R_{\wedge}(t, \bA_t)] \\
 %    % &\qquad \EE \left[ \left. R_{\wedge}(t, \bA_t) \EE \left[ \left. \frac{1}{p_{\wedge, t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right] \\
 %    \end{align*}
 %    and anaylize our problem under the assumption that all items in $\bA_t$ are observed.

\end{proof}

@@

The more items the learning agent reveals, the more reward the agent should receive. It is reasonable to assume that
$$
1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0.
$$
At the end of time $t$, the learning agent observes $\bO_{t}, \bw_t(\ba_k^t), k \leq \bO_{t}$ and receives reward $\br_{t}$:
\begin{align*}
	\br_{t} &= \begin{cases}
		1 - \gamma_{\bO_{t}}  &\text{if } \bw_t(\ba_{\bO_{\wedge, t}}^t) = 0,\\
		1 &\text{if } \bw_t(\ba_{\bO_{\wedge, t}}^t) = 1,
	\end{cases}\\
	&=\begin{cases}
		1-\gamma_{k}  &\text{if } \bw_t(\ba_{i}^t) = 1, i < k, \bw_t(\ba_{k}^t) = 0,\\
		1 &\text{if } \bw_t(\ba_{i}^t) = 1, i\leq \abs{\bA_t}.
	\end{cases}
\end{align*}

@@

In the problem of network transportations or sequential task processing, $p^*$ defined above might be very small. So we have the following improvements. Suppose we also consider position discount here.  
\begin{theorem} %main theorem
	\label{thm:and}
	Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_{K} \geq 0$ and $\gamma_k' = 1 - \gamma_k, \gamma'_K \leq \frac{1}{4} f_{\wedge}^{\ast}$. 
	Let regularization parameter $\lambda$ satisfy $\lambda \geq C_\gamma$, where $C_\gamma = \sum_{k=1}^{K} \gamma_k^2$. 
	Then for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regrets of our algorithm, C$^3$-UCB for both the conjunctive and disjunctive objectives, satisfy
	\begin{align}
	R_{\wedge}(T) &\le \frac{\sqrt{128}}{f_{\wedge}^{\ast}} \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))} \nonumber \\
	&\qquad \cdot \left(\sqrt{d\ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^{2/d}}\right) } + \sqrt{\lambda}\right) \nonumber \\
	&=O\left(\frac{d}{f_{\wedge}^{\ast}}\sqrt{TK} \ln \left(\frac{C_\gamma T}{\delta^{2/d}}\right) \right).
	\end{align}
\end{theorem}

The proof of this theorem is different in the following lemmas.

  Then we use a prefix to replace $\bA_t$ such that the probability of observing all items is close to $f_{\wedge}^{\ast}$ and the gaps are close to those of the original solutions.
  \begin{lemma}
    \CLemmaPrefixExi
  \end{lemma}
  Then we use the prefix to replace $\bA_t$ to compute the expected regret. 
  Next we need to show the expected reward function is increasing with respect to $w$ when $\gamma~s$ are decreasing and $\gamma's$ are increasing and bound $f(\bA_t, \bU_t)$ and $f_{\wedge}(\bB_t, \bU_t)$ which is non-linear and contains discounted parameters $\gamma$.
  \begin{lemma}
  	%\CLemmaIncre
  \end{lemma}
  \begin{lemma}
  	%\CLemmaTech
  \end{lemma}
  From the above Lemmas, the cumulative regret is bounded by the discounted sum of the contextual information of observed base arms in $\bV$-norms. The next two Lemmas solve this issue.
  \begin{lemma}
  	\CLemmaSumXiEstimateInDet
  \end{lemma}
  \begin{lemma}
  	\CLemmaDetVt
  \end{lemma}
  Then we can use a mean inequality to derive the result.

@@

@@

\begin{proof}[ of Theorem \ref{thm:main}]
	Suppose inequality (\ref{eq:estimateTheta}) holds for all time $t$, which is true with probability $1-\delta$. Then we have
	\begin{align}
	&R(T) = \EE \left[\sum_{t=1}^{n} \EE_{t}[R(t, \bA_t)] \right] \notag\\
	&\leq \EE\left[\sum_{t=1}^{n} \frac{1}{p^*} \EE_t \left[\bbeta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\right] \right] \label{eq:pfMdeltaEst}\\
	&\leq \EE\left[\sum_{t=1}^{n} \frac{1}{p^*} \bbeta_{T}(\delta) \EE_t \left[ \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\right] \right] \label{eq:pfMbeta}\\
	&\leq \EE \left[\frac{1}{p^*} \bbeta_T(\delta) \sqrt{\left(\sum_{t=1}^{n} \bO_t\right) \left( \sum_{t=1}^{n} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right)} \right ]  \label{eq:pfMmeanEq}\\
	&\leq \EE\left[\frac{1}{p^*} \left( \sqrt{ \ln \left( \frac{\det(\bV_T)}{\lambda^d \delta^2} \right)} + \sqrt{\lambda} \right) \right. \notag\\
	& \left. \qquad \qquad \cdot \sqrt{nK \cdot 2\ln \left(\frac{\det(\bV_T)}{\lambda^d} \right)} \right] \label{eq:pfMsumXi}\\
	&\leq \frac{\sqrt{2}}{p^*} \left(\sqrt{ d \ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^{2/d}} \right) } + \sqrt{\lambda} \right) \notag\\
	&\qquad \qquad \cdot \sqrt{nKd\ln(1 + C_\gamma T/(\lambda d))}. \label{eq:pfMdetEst}
	\end{align}
	Inequality \eqref{eq:pfMdeltaEst} is by Lemma \ref{lem:DeltaEsimateWithP*}. 
	Inequality \eqref{eq:pfMbeta} is because $\bbeta_{t}(\delta)$ is increasing with respect to $t$, derived by the definition of $\bbeta_t(\delta)$ (Eq.\eqref{eq:definebeta}) and Lemma \ref{lem:detVt}. 
	Inequality \eqref{eq:pfMmeanEq} is by the mean inequality. 
	Inequality \eqref{eq:pfMsumXi} is because of the definition of $\bbeta_t(\delta)$ (Eq.\eqref{eq:definebeta}) and Lemma \ref{lem:SumXiEstimateInDet}. 
	And the last inequality \eqref{eq:pfMdetEst} is because estimate of $\det(\bV_t)$ by Lemma \ref{lem:detVt}.
\end{proof}

@@

\begin{lemma}[monotonicity]
	Suppose $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$. Then $f(A, w)$ is increasing with respect to $w$; that is, if $0 \leq w \leq w' \leq 1$ as column vectors in $\RR^L$, then for any $A \in \prod^{\leq K}$, it holds that
	$$
	f(A, w) \leq f(A, w').
	$$
\end{lemma}
\begin{proof}
	Denote $A = (a_1, \ldots, a_{|A|})$. Because
	\begin{align*}
	&1 - f(A, 1-w) \\
	=& 1- \sum_{k = 1}^{\abs{A}} (1 - \gamma_k) \prod_{i = 1}^{k - 1} (1-w(a_i))w(a_k) - \prod_{i=1}^{\abs{A}}(1-w(a_i))\\
	=& \sum_{k = 1}^{\abs{A}} \gamma_{k} \prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k),
	\end{align*}
	then by the proof of Lemma \ref{lem:orMonotonicity} and $1-f(A,1-w)$ is increasing in $w$, we can get $f$ is increasing in $w$.
\end{proof}

\begin{lemma}[Lipschitz continuity]
	Suppose $0 \leq \gamma_k \leq 1, k \leq K$. Let $w, w'\in [0,1]^{L}$. Then
	$$
	|f(A, w) - f(A, w')| \leq \sum_{k=1}^{|A|} \gamma_k |w(a_k) - w'(a_k)|,
	$$
	where $A = (a_1, \ldots, a_{|A|})$.
\end{lemma}
\begin{proof}
	Similar to the proof of Lemma \ref{lem:orLip}. It is enough to prove when $w \leq w', w' = w + v $ and $A = (1, \ldots, m), m \leq K$.

@@

%   If we have
%   $$
%     \gamma_K' \le \frac{1}{4} f_{\wedge}^{\ast} = \frac{1}{4} \min_{1 \leq t \leq T} f_{\wedge, t}^{\ast},
%   $$
%   then
%   $$
%     \EE_t [R_{\wedge}(t, \bA_t) ] \leq \frac{8}{f_{\wedge}^{\ast}} \EE_t \left[ \bbeta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
%   $$

>>>>

\newcommand{\CLemmaPrefixExi}{
	Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0$. Let $A = (a_1, ..., a_{\abs{A}})$. For the time $t$ and the conjunctive objective, there exists a prefix $B$ of $A$ such that 
	$$
	p_{t, B} \geq \frac{1}{2}f_{t}^{\ast} - 1 + \gamma_{\abs{B}}, \qquad R(t, B) \geq \frac{1}{2} R(t, A).
	$$ 
}
\newcommand{\CEqDeltaEstAnd}{
	$$
	\EE_t [R(t, \bA_t) ] \leq \frac{8}{f^{\ast}} \EE_t \left[ \bbeta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
	$$
}
\newcommand{\CLemmaSumXiEstimateInDet}{
  If $\lambda \geq C_\gamma$, then
  $$
    \sum_{s=1}^t \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2\ln \left(\frac{\det(\bV_t)}{\lambda^d} \right).
  $$
}
\newcommand{\CLemmaDetVt}{
  $\det(\bV_t)$ is increasing with respect to $t$ and 
  $$
    \det(\bV_t) \leq (\lambda + C_\gamma t/d)^d.
  $$
}

@@

Usually in recommendations, different positions have different values. It is natural to introduce position discounts.

@@

The main contributions of this paper can be listed as follows: (1) We propose a general framework called contextual combinatorial cascading bandit that can address recommendation problem and network routing problem; (2) We propose $C^3$-UCB, an efficient algorithm for contextual combinatorial cascading bandit, with regret bound as $\tilde{O}(\sqrt{n})$ for $n$ rounds; (3) We evaluate this algorithm on synthetic data, recommendation data and network routing data and the results show that our algorithm is effective.

@@

Our work generalizes combinatorial cascading bandits of \cite{kveton2015combinatorial} to involve contextual information and position discount. Our generalization expands the applicability of this model and we evaluate it on two real-world problems. \cite{kveton2015cascading} introduced the cascading model to the multi-armed bandit framework and the feasible set is a uniform matroid. They found that recommending items in increasing order of their UCBs has a better performance than in decreasing order of their UCBs; the reason might be that the items with lower preference come first, so the learning agent will collect more data. However, this might have problem in real applications; to improve the quality of user experience, it is natural to list items with higher preference first and then lower preference items. Our work extends this part by introducing position discounted parameters. Under our setting, the items with higher UCB will come first. \cite{combes2015learning} considers a similar recommendation model to cascading bandits with position discount but they assume that a user is interested in a single topic only. In our setting, users and items are represented by feature vectors which is more general.

Our work considers contextual combinatorial bandits with cascading feedback and nonlinear reward. \cite{li2010contextual} studied multi-armed bandit with context information. \cite{qin2014contextual} introduced contextual combinatorial bandit with semi-bandit feedback and nonlinear reward. Their setting is more informative than ours and we have generalized their model with a theoretical regret bound.

@@

A newer version of \cite{chen2013combinatorial} considers probabilistic triggering base arms in stochastic combinatorial semi-bandit. When a super arm $S$ is pulled, base arm $i$ might also be triggered with a probability $p_i^{S}$. Our setting is more specific than theirs. The base arms in a super arm are triggered in list order; only the previous ones are triggered, the base arm can have the chance to be triggered.
Also, they don't consider the contextual information and position discounts.

@@

Let $\cH_t$ denote the history before the learning agent chooses action at time $t$. Thus $\cH_t$ contains all information as well as observations at time $s < t$ and context information at time $t$. Given history $\cH_t$, we assume $\bw_{t,a}$'s are mutually independent and satisfy
\begin{equation} % eq:expectation
  \label{eq:expectation}
  \EE[\bw_{t,a} | \cH_t] = \theta_{\ast}^{\top} x_{t,a},
\end{equation}
where $\theta_{\ast}$ is an unknown $d$-dimensional vector with the assumption that $\norm{\theta_{\ast}}_2 \leq 1$ and $0 \leq \theta_{\ast}^{\top} x_{t,a} \leq 1$ for all $t, a$. Define $w_{t,a} = \theta_{\ast}^{\top} x_{t,a}$ as the expected weight of base arm $a$ at time $t$. Following standard assumptions of stochastic MABs, we assume that all reward distributions have R-sub-Gaussian tails for some known constant $R > 0$; formally, for all $\lambda \in \RR$, one has 
$$
\EE[\exp(\lambda(\bw_{t,a} - \theta_{\ast}^{\top} x_{t,a})) | \cH_t] \leq \exp(\lambda^2 R^2)/2.
$$

@@

\begin{lemma} $\mathrm{\cite{abbasi2011improved}}$ %estimate of theta
  \label{thm:theta_estimate}
  Let 
  \begin{equation}
    \bbeta_{t}(\delta) = R\sqrt{\ln\left(\frac{\det(\bV_{t})}{\lambda^d \delta^2}\right)} + \sqrt{\lambda}. \label{eq:definebeta}
  \end{equation}
  Then for any $\delta > 0$, with probability at least $1 - \delta$, for all $t > 0$, we have
  \begin{equation}
    \label{eq:estimateTheta}
    \norm{\hat{\theta}_t - \theta_{\ast}}_{\bV_{t}} \leq \bbeta_{t}(\delta).
  \end{equation}
\end{lemma}

@@

\begin{theorem} %main theorem
	\label{thm:main}
	Suppose the expected reward function $f(A, w)$ is a function of expected weights and satisfies the requirements of monotonicity and Lipschitz continuity. Assume there is an $\alpha$-approximation oracle $\cO_{\cS}$. Then for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regret of our algorithm, C$^3$-UCB, satisfies
	\begin{align}
		R(n) &\le \frac{\sqrt{2}}{p^*} \sqrt{TKd\ln(1 + C_\gamma n/(\lambda d))}  \nonumber \\
		&\qquad \cdot \left(R\sqrt{d\ln \left( \frac{1 + C_\gamma n/(\lambda d)}{\delta^{2/d}}\right) } + \sqrt{\lambda}\right) \nonumber \\
		&=O\left(\frac{d}{p^*} \sqrt{nK} \ln \left(\frac{C_\gamma n}{\delta^{2/d}}\right) \right).
	\end{align}
\end{theorem}
\begin{proof} [of Theorem \ref{thm:main}] %proof outline of main theorem
	The complete proof is in the Appendix. The main idea is to reduce the regret at time $t$, $R(t, \bA_t)$, to the case that all items in $\bA_t$ have been observed. This reduction is challenging for two reasons. First, our setting has contextual information. Second, we consider position-discounted weight $\gamma$.

	In particular, by monotonicity and Lipschitz continuity, we have
	$$
		R(t, \bA_t) \leq B \sum_{k=1}^{\bO_t} \bbeta_{t-1}(\delta) \gamma_k \| x_{t, \ba_k^t} \|_{\bV_{t-1}}.
	$$
	However, it is hard to estimate an upper bound for $\sum_{t=1}^T \sum_{k=1}^{\abs{\bA_t}} \norm{ x_{t, \ba_k^t} }_{ \bV_{t-1}^{-1} }$ because $\bV_t$ only contains observed base arms. Thus we need the following deduction.
	\begin{align*}
    	&\EE[R(t, \bA_t)|\cH_t] \\
    	&\qquad = \EE \left[ \left. R(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t = \abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right]\\
    	&\qquad \leq \frac{1}{p^*} \EE \left[ \left. R(t, \bA_t) \bOne\{\bO_t = \abs{\bA_t}\} \right| \cH_t \right].
    % &\EE_t[R_{\wedge}(t, \bA_t)] \\
    % &\qquad \EE \left[ \left. R_{\wedge}(t, \bA_t) \EE \left[ \left. \frac{1}{p_{\wedge, t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right] \\
    \end{align*}
    Then the cumulative regret is bounded by the discounted sum of the contextual information of observed base arms in $\bV$-norms. The next Lemma solves this issue.
    \begin{lemma}
    	\label{lem:XNormSumEst}
    	If $\lambda \geq C_{\gamma}$, then
    	$$
    	\sum_{s=1}^t \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2d\ln \left(1 + C_{\gamma}t/(\lambda d)\right),
    	$$
    \end{lemma}
    Then we can prove this theorem.
\end{proof}

@@

The more items the learning agent reveals, the more reward the agent should receive. It is reasonable to assume that
$$
1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0.
$$
At the end of time $t$, the learning agent observes $\bO_{t}, \bw_t(\ba_k^t), k \leq \bO_{t}$ and receives reward $\br_{t}$:
\begin{align*}
	\br_{t} &= \begin{cases}
		1 - \gamma_{\bO_{t}}  &\text{if } \bw_t(\ba_{\bO_{t}}^t) = 0,\\
		1 &\text{if } \bw_t(\ba_{\bO_{t}}^t) = 1,
	\end{cases}\\
	&=\begin{cases}
		1-\gamma_{k}  &\text{if } \bw_t(\ba_{i}^t) = 1, i < k, \bw_t(\ba_{k}^t) = 0,\\
		1 &\text{if } \bw_t(\ba_{i}^t) = 1, i\leq \abs{\bA_t}.
	\end{cases}
\end{align*}

@@

In the problem of network transportations or sequential task processing, $p^*$ defined above might be very small. So we have the following improvements. Suppose we also consider position discount here.  
\begin{theorem} %main theorem
	\label{thm:and}
	Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_{K} \geq 0$ and $\gamma_K \geq 1 - \frac{1}{4} f^{\ast}$. Let regularization parameter $\lambda$ satisfy $\lambda \geq C_\gamma$, where $C_\gamma = \sum_{k=1}^{K} \gamma_k^2$. Then for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regret of our algorithm, C$^3$-UCB for the conjunctive objective, satisfies
	\begin{align}
		R(n) \le& \frac{\sqrt{128}}{f^{\ast}} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))} \nonumber \\
		&\qquad \cdot \left(\sqrt{d\ln \left( \frac{1 + C_\gamma n/(\lambda d)}{\delta^{2/d}}\right) } + \sqrt{\lambda}\right) \nonumber \\
		=&O\left(\frac{d}{f^{\ast}}\sqrt{nK} \ln \left(\frac{C_\gamma n}{\delta^{2/d}}\right) \right).
	\end{align}
\end{theorem}
\begin{proof}
	We will prove it in the appendix. The main idea is that we prove the expected reward function satisfies the properties of monotonicity and Lipschitz continuity first. And then use the following lemma to replace $\bA_t$ with a prefix.
	\begin{lemma}
		\CLemmaPrefixExi
	\end{lemma}

	Therefore we can get
	\CEqDeltaEstAnd

	Then similar to the proof of Theorem \ref{thm:main} and by the Lemma \ref{lem:XNormSumEst}, we can prove this theorem.
\end{proof}

@@

1. Our setting generalizes theirs, and our results with restricted to theirs is of same order except log

2. there is also other problem that can't be explained in their model even if without context information

@@

\begin{proof}[ of Theorem \ref{thm:main}]
	Suppose inequality (\ref{eq:estimateTheta}) holds for all time $t$, which is true with probability $1-\delta$. Then we have
	\begin{align}
	&R(T) = \EE \left[\sum_{t=1}^{n} \EE_{t}[R(t, \bA_t)] \right] \notag\\
	&\leq \EE\left[\sum_{t=1}^{n} \frac{1}{p^*} \EE_t \left[\bbeta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\right] \right] \label{eq:pfMdeltaEst}\\
	&\leq \EE\left[\sum_{t=1}^{n} \frac{1}{p^*} \bbeta_{T}(\delta) \EE_t \left[ \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\right] \right] \label{eq:pfMbeta}\\
	&\leq \EE \left[\frac{1}{p^*} \bbeta_T(\delta) \sqrt{\left(\sum_{t=1}^{n} \bO_t\right) \left( \sum_{t=1}^{n} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right)} \right ]  \label{eq:pfMmeanEq}\\
	&\leq \EE\left[\frac{1}{p^*} \left( R \sqrt{ \ln \left( \frac{\det(\bV_n)}{\lambda^d \delta^2} \right)} + \sqrt{\lambda} \right) \right. \notag\\
	& \left. \qquad \qquad \cdot \sqrt{nK \cdot 2\ln \left(\frac{\det(\bV_n)}{\lambda^d} \right)} \right] \label{eq:pfMsumXi}\\
	&\leq \frac{\sqrt{2}}{p^*} \left(R\sqrt{ d \ln \left( \frac{1 + C_\gamma n/(\lambda d)}{\delta^{2/d}} \right) } + \sqrt{\lambda} \right) \notag\\
	&\qquad \qquad \cdot \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}. \label{eq:pfMdetEst}
	\end{align}
	Inequality \eqref{eq:pfMdeltaEst} is by Lemma \ref{lem:DeltaEsimateWithP*}. 
	Inequality \eqref{eq:pfMbeta} is because $\bbeta_{t}(\delta)$ is increasing with respect to $t$, derived by the definition of $\bbeta_t(\delta)$ (Eq.\eqref{eq:definebeta}) and Lemma \ref{lem:detVt}. 
	Inequality \eqref{eq:pfMmeanEq} is by the mean inequality. 
	Inequality \eqref{eq:pfMsumXi} is because of the definition of $\bbeta_t(\delta)$ (Eq.\eqref{eq:definebeta}) and Lemma \ref{lem:SumXiEstimateInDet}. 
	And the last inequality \eqref{eq:pfMdetEst} is because estimate of $\det(\bV_t)$ by Lemma \ref{lem:detVt}.
\end{proof}

@@

\begin{lemma}[monotonicity]
	\label{lem:andMonotonicity}
	Suppose $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$. Then $f(A, w)$ is increasing with respect to $w$; that is, if $0 \leq w \leq w' \leq 1$ as column vectors in $\RR^L$, then for any $A \in \prod^{\leq K}$, it holds that
	$$
	f(A, w) \leq f(A, w').
	$$
\end{lemma}
\begin{proof}
	Denote $A = (a_1, \ldots, a_{|A|})$. Because
	\begin{align*}
	&1 - f(A, 1-w) \\
	=& 1- \sum_{k = 1}^{\abs{A}} (1 - \gamma_k) \prod_{i = 1}^{k - 1} (1-w(a_i))w(a_k) - \prod_{i=1}^{\abs{A}}(1-w(a_i))\\
	=& \sum_{k = 1}^{\abs{A}} \gamma_{k} \prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k),
	\end{align*}
	then by the proof of Lemma \ref{lem:orMonotonicity} and $1-f(A,1-w)$ is increasing in $w$, we can get $f$ is increasing in $w$.
\end{proof}

\begin{lemma}[Lipschitz continuity]
	\label{lem:andLip}
	Suppose $0 \leq \gamma_k \leq 1, k \leq K$. Let $w, w'\in [0,1]^{L}$. Then
	$$
	|f(A, w) - f(A, w')| \leq \sum_{k=1}^{|A|} \gamma_k |w(a_k) - w'(a_k)|,
	$$
	where $A = (a_1, \ldots, a_{|A|})$.
\end{lemma}
\begin{proof}
	Similar to the proof of Lemma \ref{lem:orLip}. It is enough to prove when $w \leq w', w' = w + v $ and $A = (1, \ldots, m), m \leq K$.

@@

The key difference from the proof of Theorem \ref{thm:main} is the following lemma. This lemma corresponds to Lemma \ref{lem:DeltaEsimateWithP*} and uses $f^{\ast}$ to replace $p^{\ast}$.

\begin{lemma}
	If we have $\gamma_K \geq 1 -  \frac{1}{4} f^{\ast}$, where $f^{\ast} = \min_{1 \leq t \leq T} f_{t}^{\ast}$, then
	\CEqDeltaEstAnd
\end{lemma}
\begin{proof}
	By Lemma~\ref{lem:prefixexists} there exists a prefix $\bB_t$ of $\bA_t$ such that $p_{t, \bB_t} \geq \frac{1}{2}f_{t}^* - 1 + \gamma_{|\bB_t|}$ and $R(t, \bB_t) \geq \frac{1}{2} R(t, \bA_t)$. By the assumption that $1-\gamma_{|\bB_t|} \leq 1-\gamma_K \leq \frac{1}{4} f^{\ast} \leq \frac{1}{4} f^*_{t}  $, we have $p_{t, \bB_t} \geq \frac{1}{4}f_{t}^*$.
